Design and Implementation of\\Anglican Probabilistic Programming Language

### 2016-09-01 slides/slides.tex
proper structure

\begin{frame}[fragile]{Example: Model Selection}
\begin{minted}[linenos, fontsize=\small]{clojure}
(let [;; Guessing a distribution
      dist (sample (categorical
                     [[normal 1] [gamma 1]
                      [uniform-continuous 1]
                      [uniform-discrete 1]]))
      a (sample (gamma 1 1))
      b (sample (gamma 1 1))
      d (dist a b)]

  ;; Observing samples from the distribution
  (loop [data data]
    (when (seq data)
      (let [[x & data] data]
        (observe d x))
      (recur data)))

  ;; Predicting a, b and the distribution
  (predict :a a) 
  (predict :b b)
  (predict :d d))
\end{minted}
\end{frame}

@@

\subsection{Language}

\subsection{Macro-based compilation}

\subsection{Implementation Highlights}

\subsection{Managing stack size}

\subsection{Probabilistic forms}

\subsection{Memoization}

>>>>

\begin{frame}[fragile]{Example: Model Selection}
\begin{minted}[linenos, fontsize=\small]{clojure}
(let [;; Guessing a distribution
      dist (sample (categorical
                     [[normal 1] [gamma 1]
                      [uniform-continuous 1]
                      [uniform-discrete 1]]))
      a (sample (gamma 1 1))
      b (sample (gamma 1 1))
      d (dist a b)]
  ;; Observing samples from the distribution
  (loop [data data]
    (when (seq data)
      (let [[x & data] data]
        (observe d x))
      (recur data)))
  ;; Predicting a, b and the distribution
  (predict :a a) 
  (predict :b b)
  (predict :d d))
\end{minted}
\end{frame}

@@

\begin{frame}{Language}
\end{frame}

\begin{frame}{Macro-based compilation}
\end{frame}

\section{Implementation Highlights}

\begin{frame}{Managing stack size}
\end{frame}

\begin{frame}{Probabilistic forms}
\end{frame}

\begin{frame}{Memoization}
\end{frame}
